\newpage\documentclass[11pt,onecolumn,fleqn]{article}

\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage[hang,flushmargin]{footmisc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{xcolor}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\setlength{\oddsidemargin}{0pt}
\setlength{\textwidth}{460pt}
\setlength{\voffset}{-1cm}
\setlength{\textheight}{21cm}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\newcommand{\TT}{$\checkmark$}
\newcommand{\FF}{$\times$}

\def\fall#1{\forall\, {#1}\,}
\def\fex#1{\exists \,{#1}\,}
\def\fexone#1{\exists_{1} \,{#1}\,}
\def\fmlmat#1{\bigl(\,{#1}\,\bigr)}

\def\set#1#2{\{\, {#1} \mid {#2}\,\}}

\begin{document}
\thispagestyle{empty}
\begin{center}
{\Huge
21-128 and 15-151 problem sheet 3
}

Solutions to the following seven exercises and optional bonus problem are to be submitted through 
gradescope by 11PM on

\textbf{Wednesday 21st September 2022.}

\end{center}


\subsubsection*{Problem 1}
Consider a function $f : A \to A$. Prove that if $f \circ f$ is injective, then $f$ is injective.


\subsubsection*{Problem 2}
Consider functions $f : A \to B$ and $g : B \to A$. Prove that
\begin{enumerate}[(a)]
\item If $f \circ g$ is the identity function on $B$, then $f$ is surjective.
\item If $g \circ f$ is the identity function on $A$, then $f$ is injective.
\end{enumerate}

\textit{To remind you: given a set $X$, the identity function on $X$ is the function $\mathrm{id}_X : X \to X$ 
defined by $\mathrm{id}_X(x)=x$ for all $x \in X$.}

\subsubsection*{Problem 3}
Let $a,b,c,d \in \mathbb{R}$ be constants with $a \ne 0$ and $c \ne 0$. Suppose that $f,g : \mathbb{R} \to \mathbb{R}$ with 
$f(x)=ax+b$ and $g(x)=cx+d$ for all $x \in \mathbb{R}$. Prove that $f$ and $g$ are injective and surjective, but that the 
function $h : \mathbb{R} \to \mathbb{R}$ defined by $h = g \circ f - f \circ g$ is neither injective nor surjective.

\subsubsection*{Problem 4}
Verify that the function $f : (0,1) \to \mathbb{R}$ defined by
$$f(x) = \frac{2x-1}{2x(1-x)} \quad \text{for all } x \in (0,1)$$
is a bijection.


\newpage

\subsubsection*{Problem 5}
\begin{enumerate}[(a)]
    \item Let $f: \mathbb{R} \times \mathbb{R} \rightarrow \mathbb{R}$, $g: \mathbb{R} \times \mathbb{R} \rightarrow \mathbb{R}$ where $f$ and $g$ are surjective and let $h: \mathbb{R} \times \mathbb{R} \rightarrow \mathbb{R}$ s.t. $\fall{(x, y)} \in \mathbb{R} \times \mathbb{R},\ h(x, y) = f(x, y) + g(x, y)$. Determine, with proof, whether or not $h$ is necessarily surjective.
    \item For all positive integers $n$, define $S_n$ to be the set of bijections on $[n]$. Let
    \begin{align*}
      A &= \set{ f \in S_{n}}{ \fall{x \in [n]}( f(x) \neq x )} \\
      B &=  \set{ f \in S_{n}}{ \fex{g \in S_{n}} \fall{x \in [n]}( f(g(x)) \neq g(x) )}
    \end{align*}
    Show that $A = B$.
\end{enumerate}


\subsubsection*{Problem 6}
\begin{enumerate}[(a)]
    \item Find a function $f:\mathbb{N}\rightarrow\mathbb{N}$ that is surjective and not injective, and show that it has at least two right-inverses.
    \item Suppose that $f:A\rightarrow B$ is surjective but not injective. Prove that $f$ has at least two right-inverses.
\end{enumerate}


\subsubsection*{Problem 7}
Let $g : \mathbb{R} \rightarrow \mathbb{R}$ and define $f : \mathcal{P}(\mathbb{R}) \rightarrow \mathcal{P}(\mathbb{R})$ via $f(S) = \{g(x) \mid x \in S\}$. 

\begin{enumerate}
\item[a)] Determine necessary and sufficient conditions on $g$ to have
\begin{equation*}
    \fall{A, B} \subseteq \mathbb{R} \, \  f(A \cap B) = f(A) \cap f(B)
\end{equation*}

\item[b)] Show that if $g$ is surjective, then $f$ is surjective. 
\end{enumerate}


\subsubsection*{Bonus Problem - 2 points}
Let $f : A \to B$ be a function.
\begin{enumerate}[(a)]
\item Prove that there exists a set $X$ and functions $p : A \to X$ and $i : X \to B$, with $p$ surjective and $i$ injective, 
such that $f = i \circ p$.
\item Prove that there exists a set $Y$ and functions $j : A \to Y$ and $q : Y \to B$, with $j$ injective and $q$ surjective, 
such that $f = q \circ j$.
\end{enumerate}


\end{document}
